---
title: "chapter9-1"
author: "Min-Yao"
date: "2018年4月22日"
output: 
  html_document: 
    keep_md: yes
---

# Chapter 9 Lab: Support Vector Machines

# Support Vector Classifier

```{r}
#video
set.seed(10111)
x=matrix(rnorm(40),20,2)
y=rep(c(-1,1),c(10,10))
x[y==1,]=x[y==1,] + 1
plot(x, col=y+3,pch=19)

library(e1071)
dat=data.frame(x,y=as.factor(y))
svmfit=svm(y~., data=dat, kernel="linear", cost=10,scale=FALSE)
print(svmfit)
plot(svmfit, dat)

make.grid=function(x,n=75){
  grange=apply(x,2,range)
  x1=seq(from=grange[1,1],to=grange[2,1],length=n)
  x2=seq(from=grange[1,2],to=grange[2,2],length=n)
  expand.grid(X1=x1,X2=x2)
}
xgrid=make.grid(x)
ygrid=predict(svmfit,xgrid)
plot(xgrid,col=c("red","blue")[as.numeric(ygrid)],pch=20,cex=.2)
points(x,col=y+3,pch=19)
points(x[svmfit$index,],pch=5,cex=2)

beta=drop(t(svmfit$coefs)%*%x[svmfit$index,])
beta0=svmfit$rho
plot(xgrid,col=c("red","blue")[as.numeric(ygrid)],pch=20,cex=.2)
points(x,col=y+3,pch=19)
points(x[svmfit$index,],pch=5,cex=2)
abline(beta0/beta[2],-beta[1]/beta[2])
abline((beta0-1)/beta[2],-beta[1]/beta[2],lty=2)
abline((beta0+1)/beta[2],-beta[1]/beta[2],lty=2)
#
set.seed(1)
x=matrix(rnorm(20*2), ncol=2)
y=c(rep(-1,10), rep(1,10))
x[y==1,]=x[y==1,] + 1
plot(x, col=(3-y))
dat=data.frame(x=x, y=as.factor(y))

library(e1071)
svmfit=svm(y~., data=dat, kernel="linear", cost=10,scale=FALSE)
plot(svmfit, dat)

svmfit$index
summary(svmfit)
svmfit=svm(y~., data=dat, kernel="linear", cost=0.1,scale=FALSE)
plot(svmfit, dat)
svmfit$index
set.seed(1)
tune.out=tune(svm,y~.,data=dat,kernel="linear",ranges=list(cost=c(0.001, 0.01, 0.1, 1,5,10,100)))
summary(tune.out)
bestmod=tune.out$best.model
summary(bestmod)
xtest=matrix(rnorm(20*2), ncol=2)
ytest=sample(c(-1,1), 20, rep=TRUE)
xtest[ytest==1,]=xtest[ytest==1,] + 1
testdat=data.frame(x=xtest, y=as.factor(ytest))
ypred=predict(bestmod,testdat)
table(predict=ypred, truth=testdat$y)
svmfit=svm(y~., data=dat, kernel="linear", cost=.01,scale=FALSE)
ypred=predict(svmfit,testdat)
table(predict=ypred, truth=testdat$y)
x[y==1,]=x[y==1,]+0.5
plot(x, col=(y+5)/2, pch=19)
dat=data.frame(x=x,y=as.factor(y))
svmfit=svm(y~., data=dat, kernel="linear", cost=1e5)
summary(svmfit)
plot(svmfit, dat)
svmfit=svm(y~., data=dat, kernel="linear", cost=1)
summary(svmfit)
plot(svmfit,dat)
```

# Support Vector Machine

```{r}
set.seed(1)
x=matrix(rnorm(200*2), ncol=2)
x[1:100,]=x[1:100,]+2
x[101:150,]=x[101:150,]-2
y=c(rep(1,150),rep(2,50))
dat=data.frame(x=x,y=as.factor(y))
plot(x, col=y)
train=sample(200,100)
svmfit=svm(y~., data=dat[train,], kernel="radial",  gamma=1, cost=1)
plot(svmfit, dat[train,])
summary(svmfit)
svmfit=svm(y~., data=dat[train,], kernel="radial",gamma=1,cost=1e5)
plot(svmfit,dat[train,])
set.seed(1)
tune.out=tune(svm, y~., data=dat[train,], kernel="radial", ranges=list(cost=c(0.1,1,10,100,1000),gamma=c(0.5,1,2,3,4)))
summary(tune.out)
table(true=dat[-train,"y"], pred=predict(tune.out$best.model,newdata=dat[-train,]))
```

# ROC Curves

```{r}
library(ROCR)
rocplot=function(pred, truth, ...){
   predob = prediction(pred, truth)
   perf = performance(predob, "tpr", "fpr")
   plot(perf,...)}
svmfit.opt=svm(y~., data=dat[train,], kernel="radial",gamma=2, cost=1,decision.values=T)
fitted=attributes(predict(svmfit.opt,dat[train,],decision.values=TRUE))$decision.values
par(mfrow=c(1,2))
rocplot(fitted,dat[train,"y"],main="Training Data")
svmfit.flex=svm(y~., data=dat[train,], kernel="radial",gamma=50, cost=1, decision.values=T)
fitted=attributes(predict(svmfit.flex,dat[train,],decision.values=T))$decision.values
rocplot(fitted,dat[train,"y"],add=T,col="red")
fitted=attributes(predict(svmfit.opt,dat[-train,],decision.values=T))$decision.values
rocplot(fitted,dat[-train,"y"],main="Test Data")
fitted=attributes(predict(svmfit.flex,dat[-train,],decision.values=T))$decision.values
rocplot(fitted,dat[-train,"y"],add=T,col="red")
```

# SVM with Multiple Classes

```{r}
set.seed(1)
x=rbind(x, matrix(rnorm(50*2), ncol=2))
y=c(y, rep(0,50))
x[y==0,2]=x[y==0,2]+2
dat=data.frame(x=x, y=as.factor(y))
par(mfrow=c(1,1))
plot(x,col=(y+1))
svmfit=svm(y~., data=dat, kernel="radial", cost=10, gamma=1)
plot(svmfit, dat)
```

# Application to Gene Expression Data

```{r}
library(ISLR)
names(Khan)
dim(Khan$xtrain)
dim(Khan$xtest)
length(Khan$ytrain)
length(Khan$ytest)
table(Khan$ytrain)
table(Khan$ytest)
dat=data.frame(x=Khan$xtrain, y=as.factor(Khan$ytrain))
out=svm(y~., data=dat, kernel="linear",cost=10)
summary(out)
table(out$fitted, dat$y)
dat.te=data.frame(x=Khan$xtest, y=as.factor(Khan$ytest))
pred.te=predict(out, newdata=dat.te)
table(pred.te, dat.te$y)
```

# 9.7 Exercises
## Conceptual
## 1. This problem involves hyperplanes in two dimensions.
### (a) Sketch the hyperplane 1 + 3X 1 − X 2 = 0. Indicate the set of points for which 1 + 3X 1 − X 2 > 0, as well as the set of points for which 1 + 3X 1 − X 2 < 0.

### (b) On the same plot, sketch the hyperplane − 2 + X 1 + 2X 2 = 0. Indicate the set of points for which − 2 + X 1 + 2X 2 > 0, as well as the set of points for which − 2 + X 1 + 2X 2 < 0.

## 3. Here we explore the maximal margin classiﬁer on a toy data set.
### (a) We are given n = 7 observations in p = 2 dimensions. For each observation, there is an associated class label. Sketch the observations.

### (b) Sketch the optimal separating hyperplane, and provide the equation for this hyperplane (of the form (9.1)).

### (c) Describe the classiﬁcation rule for the maximal margin classiﬁer. It should be something along the lines of “Classify to Red if β 0 + β 1 X 1 + β 2 X 2 > 0, and classify to Blue otherwise.” Provide the values for β 0 , β 1 , and β 2 .

### (d) On your sketch, indicate the margin for the maximal margin hyperplane.

### (e) Indicate the support vectors for the maximal margin classiﬁer.

### (f) Argue that a slight movement of the seventh observation would not aﬀect the maximal margin hyperplane.

### (g) Sketch a hyperplane that is not the optimal separating hyperplane, and provide the equation for this hyperplane.

### (h) Draw an additional observation on the plot so that the two classes are no longer separable by a hyperplane.

## Applied
## 6. At the end of Section 9.6.1, it is claimed that in the case of data that is just barely linearly separable, a support vector classiﬁer with a small value of cost that misclassiﬁes a couple of training observations may perform better on test data than one with a huge value of cost that does not misclassify any training observations. You will now investigate this claim.

### (a) Generate two-class data with p = 2 in such a way that the classes are just barely linearly separable.

### (b) Compute the cross-validation error rates for support vector classiﬁers with a range of cost values. How many training errors are misclassiﬁed for each value of cost considered, and how does this relate to the cross-validation errors obtained?

### (c) Generate an appropriate test data set, and compute the test errors corresponding to each of the values of cost considered. Which value of cost leads to the fewest test errors, and how does this compare to the values of cost that yield the fewest training errors and the fewest cross-validation errors?

### (d) Discuss your results.

## 7. In this problem, you will use support vector approaches in order to predict whether a given car gets high or low gas mileage based on the Auto data set.
### (a) Create a binary variable that takes on a 1 for cars with gas mileage above the median, and a 0 for cars with gas mileage below the median.

### (b) Fit a support vector classiﬁer to the data with various values of cost, in order to predict whether a car gets high or low gas mileage. Report the cross-validation errors associated with different values of this parameter. Comment on your results.

## 8. This problem involves the OJ data set which is part of the ISLR package.
### (a) Create a training set containing a random sample of 800 observations, and a test set containing the remaining observations.

### (b) Fit a support vector classiﬁer to the training data using cost=0.01, with Purchase as the response and the other variables as predictors. Use the summary() function to produce summary statistics, and describe the results obtained.

### (c) What are the training and test error rates?

### (d) Use the tune() function to select an optimal cost. Consider values in the range 0.01 to 10.

### (e) Compute the training and test error rates using this new value for cost.