---
title: "chapter4-1"
author: "Min-Yao"
date: "2018年1月16日"
output: 
  html_document: 
    keep_md: yes
---
# Chapter 4 Lab: Logistic Regression, LDA, QDA, and KNN

# The Stock Market Data

```{r}
library(ISLR)
names(Smarket)
dim(Smarket)
summary(Smarket)
pairs(Smarket)
#cor(Smarket)
cor(Smarket[,-9])
attach(Smarket)
plot(Volume)
```

# Logistic Regression

```{r}
glm.fits=glm(Direction~Lag1+Lag2+Lag3+Lag4+Lag5+Volume,data=Smarket,family=binomial)
summary(glm.fits)
coef(glm.fits)
summary(glm.fits)$coef
summary(glm.fits)$coef[,4]
glm.probs=predict(glm.fits,type="response")
glm.probs[1:10]
contrasts(Direction)
glm.pred=rep("Down",1250)
glm.pred[glm.probs>.5]="Up"
table(glm.pred,Direction)
(507+145)/1250
mean(glm.pred==Direction)
train=(Year<2005)
Smarket.2005=Smarket[!train,]
dim(Smarket.2005)
Direction.2005=Direction[!train]
glm.fits=glm(Direction~Lag1+Lag2+Lag3+Lag4+Lag5+Volume,data=Smarket,family=binomial,subset=train)
glm.probs=predict(glm.fits,Smarket.2005,type="response")
glm.pred=rep("Down",252)
glm.pred[glm.probs>.5]="Up"
table(glm.pred,Direction.2005)
mean(glm.pred==Direction.2005)
mean(glm.pred!=Direction.2005)
glm.fits=glm(Direction~Lag1+Lag2,data=Smarket,family=binomial,subset=train)
glm.probs=predict(glm.fits,Smarket.2005,type="response")
glm.pred=rep("Down",252)
glm.pred[glm.probs>.5]="Up"
table(glm.pred,Direction.2005)
mean(glm.pred==Direction.2005)
106/(106+76)
predict(glm.fits,newdata=data.frame(Lag1=c(1.2,1.5),Lag2=c(1.1,-0.8)),type="response")
```

6. Suppose we collect data for a group of students in a statistics class
with variables X 1 = hours studied, X 2 = undergrad GPA, and Y =
receive an A. We ﬁt a logistic regression and produce estimated
coeﬃcient,
ˆ
β 0 = − 6,
ˆ
β 1 = 0.05,
ˆ
β 2 = 1.
(a) Estimate the probability that a student who studies for 40 h and
has an undergrad GPA of 3.5 gets an A in the class.
(b) How many hours would the student in part (a) need to study to
have a 50 % chance of getting an A in the class?

10. This question should be answered using the Weekly data set, which
is part of the ISLR package. This data is similar in nature to the
Smarket data from this chapter’s lab, except that it contains 1, 089
weekly returns for 21 years, from the beginning of 1990 to the end of
2010.
(a) Produce some numerical and graphical summaries of the Weekly
data. Do there appear to be any patterns?
(b) Use the full data set to perform a logistic regression with
Direction as the response and the ﬁve lag variables plus Volume
as predictors. Use the summary function to print the results. Do
any of the predictors appear to be statistically signiﬁcant? If so,
which ones?
(c) Compute the confusion matrix and overall fraction of correct
predictions. Explain what the confusion matrix is telling you
about the types of mistakes made by logistic regression.
(d) Now ﬁt the logistic regression model using a training data period
from 1990 to 2008, with Lag2 as the only predictor. Compute the
confusion matrix and the overall fraction of correct predictions
for the held out data (that is, the data from 2009 and 2010).

11. In this problem, you will develop a model to predict whether a given
car gets high or low gas mileage based on the Auto data set.
(a) Create a binary variable, mpg01, that contains a 1 if mpg contains
a value above its median, and a 0 if mpg contains a value below
its median. You can compute the median using the median()
function. Note you may ﬁnd it helpful to use the data.frame()
function to create a single data set containing both mpg01 and
the other Auto variables.
(b) Explore the data graphically in order to investigate the associ-
ation between mpg01 and the other features. Which of the other
features seem most likely to be useful in predicting mpg01? Scat-
terplots and boxplots may be useful tools to answer this ques-
tion. Describe your ﬁndings.
(c) Split the data into a training set and a test set.
(f) Perform logistic regression on the training data in order to pre-
dict mpg01 using the variables that seemed most associated with
mpg01 in (b). What is the test error of the model obtained?