---
title: "chapter3-1"
author: "Min-Yao"
date: "2017年12月5日"
output: 
  html_document: 
    keep_md: yes
---

# Chapter 3 Lab: Linear Regression

```{r}
library(MASS)
library(ISLR)
```

# Simple Linear Regression

```{r}
#fix(Boston)
names(Boston)
#lm.fit=lm(medv~lstat)
lm.fit=lm(medv~lstat,data=Boston)
attach(Boston)
lm.fit=lm(medv~lstat)
lm.fit
summary(lm.fit)
names(lm.fit)
coef(lm.fit)
confint(lm.fit)
predict(lm.fit,data.frame(lstat=(c(5,10,15))), interval="confidence")
predict(lm.fit,data.frame(lstat=(c(5,10,15))), interval="prediction")

plot(lstat,medv)
abline(lm.fit)
abline(lm.fit,lwd=3)
abline(lm.fit,lwd=3,col="red")
plot(lstat,medv,col="red")
plot(lstat,medv,pch=20)
plot(lstat,medv,pch="+")
plot(1:20,1:20,pch=1:20)
par(mfrow=c(2,2))
plot(lm.fit)
plot(predict(lm.fit), residuals(lm.fit))
plot(predict(lm.fit), rstudent(lm.fit))
plot(hatvalues(lm.fit))
which.max(hatvalues(lm.fit))
```

# 8. This question involves the use of simple linear regression on the Auto data set.

(a) Use the lm() function to perform a simple linear regression with
mpg as the response and horsepower as the predictor. Use the
summary() function to print the results. Comment on the output.
For example:

```{r}
library(ISLR)
#Auto
summary(Auto)
attach(Auto)
Auto.lm.fit=lm(mpg~horsepower)
summary(Auto.lm.fit)

plot(horsepower,mpg)
abline(Auto.lm.fit,lwd=3,col="red")
```


i. Is there a relationship between the predictor and the re-
sponse?

Yes, p-value: < 2.2e-16

ii. How strong is the relationship between the predictor and
the response?

very strong, because
## Coefficients:
##              Estimate Std. Error t value Pr(>|t|)    
## (Intercept) 39.935861   0.717499   55.66   <2e-16 ***
## horsepower  -0.157845   0.006446  -24.49   <2e-16 ***

iii. Is the relationship between the predictor and the response
positive or negative?

negative, we can see their negative relationship on the plot

iv. What is the predicted mpg associated with a horsepower of
98? What are the associated 95 % conﬁdence and prediction
intervals?

```{r}
predict(Auto.lm.fit,data.frame(horsepower=98), interval="confidence")
predict(Auto.lm.fit,data.frame(horsepower=98), interval="prediction")
```


(b) Plot the response and the predictor. Use the abline() function
to display the least squares regression line.

```{r}
plot(horsepower,mpg)
abline(Auto.lm.fit,lwd=3,col="red")
```


(c) Use the plot() function to produce diagnostic plots of the least
squares regression ﬁt. Comment on any problems you see with
the ﬁt.

```{r}
par(mfrow=c(2,2))
plot(Auto.lm.fit)

```


# 13. In this exercise you will create some simulated data and will ﬁt simple linear regression models to it. Make sure to use set.seed(1) prior to starting part (a) to ensure consistent results.

(a) Using the rnorm() function, create a vector, x, containing 100
observations drawn from a N(0, 1) distribution. This represents
a feature, X.

```{r}
set.seed(1) 
#?rnorm() 
X <- rnorm(100, mean = 0, sd = 1)
X

```


(b) Using the rnorm() function, create a vector, eps, containing 100
observations drawn from a N(0, 0.25) distribution i.e. a normal
distribution with mean zero and variance 0.25.

```{r}
eps <- rnorm(100, mean = 0, sd = sqrt(0.25))
eps

```

(c) Using x and eps, generate a vector y according to the model

Y = − 1 + 0.5X + E. (3.39)

What is the length of the vector y? What are the values of β 0
and β 1 in this linear model?

> the length of the vector y is 100
> β 0= -1
> β 1= 0.5

```{r}
Y = -1 + 0.5*X + eps
Y

```


(d) Create a scatterplot displaying the relationship between x and
y. Comment on what you observe.

```{r}
plot(X,Y)

```

> linear relationship

(e) Fit a least squares linear model to predict y using x. Comment
on the model obtained. How doˆβ 0 and ˆβ 1 compare to β 0 and
β 1 ?

```{r}
XY.lm.fit <- lm(Y~X)
summary(XY.lm.fit)
confint(XY.lm.fit)
```
> β 0= -1
> β 1= 0.5
> Estimate β 0= -1.01885
> Estimate β 1= 0.49947


(f) Display the least squares line on the scatterplot obtained in (d).
Draw the population regression line on the plot, in a diﬀerent
color. Use the legend() command to create an appropriate legend.

```{r}
plot(X,Y)
abline(XY.lm.fit,lwd=3,col="red")
abline(coef= c(-1,0.5),lwd=2,col="blue")
#?abline
#?legend()
legend(-2.2,0.5, legend=c("least.squares.line", "pop.regression.line"),
       col=c("red", "blue"), lty=1, cex=0.8)

```


(g) Now ﬁt a polynomial regression model that predicts y using x
and x2. Is there evidence that the quadratic term improves the
model ﬁt? Explain your answer.

```{r}
poly.lm.fit=lm(Y ~ poly(X,2))
summary(poly.lm.fit)
confint(poly.lm.fit)
```


(h) Repeat (a)–(f) after modifying the data generation process in
such a way that there is less noise in the data. The model (3.39)
should remain the same. You can do this by decreasing the vari-
ance of the normal distribution used to generate the error term
E in (b). Describe your results.

```{r}
X2 <- rnorm(100, mean = 0, sd = 1)
X2
eps2 <- rnorm(100, mean = 0, sd = sqrt(0.01))
eps2
Y2 = -1 + 0.5*X2 + eps2
Y2

XY2.lm.fit <- lm(Y2~X2)
summary(XY2.lm.fit)
confint(XY2.lm.fit)

plot(X2,Y2)
abline(XY2.lm.fit,lwd=3,col="red")
abline(coef= c(-1,0.5),lwd=2,col="blue")
legend(-3,0.3, legend=c("least.squares.line", "pop.regression.line"),
       col=c("red", "blue"), lty=1, cex=0.8)

```


(i) Repeat (a)–(f) after modifying the data generation process in
such a way that there is more noise in the data. The model
(3.39) should remain the same. You can do this by increasing
the variance of the normal distribution used to generate the
error term E in (b). Describe your results.

```{r}
X3 <- rnorm(100, mean = 0, sd = 1)
X3
eps3 <- rnorm(100, mean = 0, sd = sqrt(1))
eps3
Y3 = -1 + 0.5*X3 + eps3
Y3

XY3.lm.fit <- lm(Y3~X3)
summary(XY3.lm.fit)
confint(XY3.lm.fit)

plot(X3,Y3)
abline(XY3.lm.fit,lwd=3,col="red")
abline(coef= c(-1,0.5),lwd=2,col="blue")
legend(-3,1, legend=c("least.squares.line", "pop.regression.line"),
       col=c("red", "blue"), lty=1, cex=0.8)
```


(j) What are the conﬁdence intervals for β 0 and β 1 based on the
original data set, the noisier data set, and the less noisy data
set? Comment on your results.

```{r}
confint(XY.lm.fit)
confint(XY2.lm.fit)
confint(XY3.lm.fit)
```

> the noisier data set has larger conﬁdence intervals for β 0 and β 1

> the less noisy data set has smaller conﬁdence intervals for β 0 and β 1

# 15. This problem involves the Boston data set, which we saw in the lab
for this chapter. We will now try to predict per capita crime rate
using the other variables in this data set. In other words, per capita
crime rate is the response, and the other variables are the predictors.

(a) For each predictor, ﬁt a simple linear regression model to predict
the response. Describe your results. In which of the models is
there a statistically signiﬁcant association between the predictor
and the response? Create some plots to back up your assertions.

```{r}
library(MASS)
summary(Boston)
names(Boston)
?Boston

attach(Boston)
lm.fit.zn=lm(crim~zn)
summary(lm.fit.zn)
lm.fit.indus=lm(crim~indus)
summary(lm.fit.indus)
lm.fit.chas=lm(crim~chas)
summary(lm.fit.chas)
lm.fit.nox=lm(crim~nox)
summary(lm.fit.nox)
lm.fit.rm=lm(crim~rm)
summary(lm.fit.rm)
lm.fit.age=lm(crim~age)
summary(lm.fit.age)
lm.fit.dis=lm(crim~dis)
summary(lm.fit.dis)
lm.fit.rad=lm(crim~rad)
summary(lm.fit.rad)
lm.fit.tax=lm(crim~tax)
summary(lm.fit.tax)
lm.fit.ptratio=lm(crim~ptratio)
summary(lm.fit.ptratio)
lm.fit.black=lm(crim~black)
summary(lm.fit.black)
lm.fit.lstat=lm(crim~lstat)
summary(lm.fit.lstat)
lm.fit.medv=lm(crim~medv)
summary(lm.fit.medv)

```

