---
title: "OJ"
author: "Min-Yao"
date: "2021/1/16"
output: 
  html_document: 
    keep_md: yes
---

## OJ

```{r}
library(tidyverse)
library(ISLR)
library(tree)
data(OJ)
?OJ
```

```{r}
OJ
summary(OJ)
```

```{r}
OJ %>% select(StoreID, STORE)
```
> StoreID and STORE are redundant
> because store is categorical we need to turn that into a series of dummy variables.

```{r}
store_cat <- OJ %>% select(StoreID) %>%
  mutate(row=1:nrow(.),data=1) %>%
  pivot_wider(id_cols = row, names_from=StoreID, values_from=data, values_fill=0, names_prefix="Store")
store_cat
```

```{r}
OJ <- OJ %>% select(-StoreID, -STORE, -Store7) %>% cbind(store_cat)
OJ
```

## (a) Create a training set containing a random sample of 800 observations, and a test set containing the remaining observations.

```{r}
set.seed(10)
train <- sample(1:nrow(OJ), size = 800)
OJ.train <- OJ[train,]
OJ.test <- OJ[-train,]
str(OJ.test)
str(OJ.train)
```

## (b) Fit a tree to the training data, with Purchase as the response and the other variables as predictors. Use the summary() function to produce summary statistics about the tree, and describe the results obtained. What is the training error rate? How many terminal nodes does the tree have?

```{r}
tree.OJ=tree(Purchase~.,OJ,subset=train)
summary(tree.OJ)
```
> Number of terminal nodes:  7

> Misclassification error rate: 0.1775

## (e) Predict the response on the test data, and produce a confusion matrix comparing the test labels to the predicted test labels. What is the test error rate?

```{r}
tree.pred=predict(tree.OJ,OJ.test,type="class")
purchase.test=OJ.test$Purchase
table(tree.pred,purchase.test)
(135+88)/270
1-((135+88)/270)
```

> Accuracy is 82.59%

## Deep learning method

```{r}
library(keras)
library(reticulate)
library(tensorflow)
use_condaenv("r-reticulate")
```

> create label

```{r}
OJ.train.label <- OJ.train %>% select(Purchase) %>% mutate(Purchase=ifelse(Purchase=="CH", 0, 1)) %>% pull(Purchase)
str(OJ.train.label)
OJ.test.label <- OJ.test %>% select(Purchase) %>% mutate(Purchase=ifelse(Purchase=="CH", 0, 1)) %>% pull(Purchase)
str(OJ.test.label)
```

> create data

```{r}
OJ.train <- OJ.train %>% select(-Purchase)
str(OJ.train)
OJ.test <- OJ.test %>% select(-Purchase)
str(OJ.test)
```

> scale it

```{r}
oj.mean <- apply(OJ.train, 2, mean)
oj.std <- apply(OJ.test, 2, sd)

OJ.train <- scale(OJ.train, center=oj.mean, scale=oj.std)
OJ.test <- scale(OJ.test, center=oj.mean, scale=oj.std)

str(OJ.train)
str(OJ.test)
```

#### Listing 3.15. Setting aside a validation set

```{r}
set.seed(10)
val_indices <- sample(1:nrow(OJ.train), size = 100)

OJ.train_val <- OJ.train[val_indices,]
partial_OJ.train <- OJ.train[-val_indices,]

# OJ.test <- data.matrix(OJ.test, rownames.force = NA)
# OJ.train <- data.matrix(OJ.train, rownames.force = NA)
# OJ.train_val <- data.matrix(OJ.train_val, rownames.force = NA)
# partial_OJ.train <- data.matrix(partial_OJ.train, rownames.force = NA)

OJ.train_val.label <- OJ.train.label[val_indices]
partial_OJ.train.label <- OJ.train.label[-val_indices]

```

### set up and run the model!

```{r}
model <- keras_model_sequential() %>% 
  layer_dense(units = 16, activation = "relu", input_shape = ncol(OJ.train) ) %>% 
  layer_dense(units = 16, activation = "relu") %>% 
  layer_dense(units = 1, activation = "sigmoid")


model %>% compile(
  optimizer = "rmsprop",
  loss = "binary_crossentropy",
  metrics = c("accuracy")
)

system.time(history <- model %>% fit(
  partial_OJ.train,
  partial_OJ.train.label,
  epochs = 100,
  batch_size = 256,
  validation_data = list(OJ.train_val, OJ.train_val.label)
))
```

```{r}
str(history)
```

```{r}
plot(history)
```

> I choose 56, run with 56 epochs and full training:

```{r}
model <- keras_model_sequential() %>% 
  layer_dense(units = 16, activation = "relu", input_shape = ncol(OJ.train) ) %>% 
  layer_dense(units = 16, activation = "relu") %>% 
  layer_dense(units = 1, activation = "sigmoid")


model %>% compile(
  optimizer = "rmsprop",
  loss = "binary_crossentropy",
  metrics = c("accuracy")
)

system.time(history <- model %>% fit(
  OJ.train,
  OJ.train.label,
  epochs = 56,
  batch_size = 256
))
```


```{r}
plot(history)
```


```{r}
results <- model %>% evaluate(OJ.test, OJ.test.label)

results
```

> Accuracy is 82.96%, which is a little bit better than the trees (82.59%).
