---
title: "chapter7-1"
author: "Min-Yao"
date: "2018年3月19日"
output: 
  html_document: 
    keep_md: yes
---

# Chapter 7 Lab: Non-linear Modeling

```{r}
library(ISLR)
attach(Wage)
```

# Polynomial Regression and Step Functions

```{r}
fit=lm(wage~poly(age,4),data=Wage)
summary(fit)
coef(summary(fit))
```

```{r}
fit2=lm(wage~poly(age,4,raw=T),data=Wage)
coef(summary(fit2))

fit2a=lm(wage~age+I(age^2)+I(age^3)+I(age^4),data=Wage)
summary(fit2a)
coef(fit2a)

plot(fitted(fit2),fitted(fit2a))

fit2b=lm(wage~cbind(age,age^2,age^3,age^4),data=Wage)
summary(fit2b)
```

```{r}
agelims=range(age)
age.grid=seq(from=agelims[1],to=agelims[2]) #min to  max (add 1 each time)
preds=predict(fit,newdata=list(age=age.grid),se=TRUE)# add SE
se.bands=cbind(preds$fit+2*preds$se.fit,preds$fit-2*preds$se.fit)

#par(mfrow=c(1,2),mar=c(4.5,4.5,1,1),oma=c(0,0,4,0))
plot(age,wage,xlim=agelims,cex=.5,col="darkgrey")
title("Degree-4 Polynomial",outer=T)
lines(age.grid,preds$fit,lwd=2,col="blue")
matlines(age.grid,se.bands,lwd=1,col="blue",lty=3)

preds2=predict(fit2,newdata=list(age=age.grid),se=TRUE)
max(abs(preds$fit-preds2$fit))
```

```{r}
fit.1=lm(wage~age,data=Wage)
fit.2=lm(wage~poly(age,2),data=Wage)
fit.3=lm(wage~poly(age,3),data=Wage)
fit.4=lm(wage~poly(age,4),data=Wage)
fit.5=lm(wage~poly(age,5),data=Wage)
anova(fit.1,fit.2,fit.3,fit.4,fit.5)

coef(summary(fit.5))
(-11.983)^2

fit.1=lm(wage~education+age,data=Wage)
fit.2=lm(wage~education+poly(age,2),data=Wage)
fit.3=lm(wage~education+poly(age,3),data=Wage)
anova(fit.1,fit.2,fit.3)
```

```{r}
#lab from video
fit=glm(I(wage>250)~poly(age,3),data=Wage,family=binomial)
summary(fit)
preds=predict(fit,newdata=list(age=age.grid),se=T)
se.bands = preds$fit + cbind(fit=0, lower=-2*preds$se, upper=2*preds$se)
se.bands[1:5,]
```

$$p=\frac{e^eta}{1+e^eta}.$$
```{r}
#lab from video
prob.bands=exp(se.bands)/(1+exp(se.bands))
matplot(age.grid, prob.bands, col = "blue", lwd = c(2,1,1),lty = c(1,2,2),type = "l",ylim = c(0,.1))
points(jitter(age),I(wage>250)/10,pch="|",cex=.5)

```



```{r}
fit=glm(I(wage>250)~poly(age,4),data=Wage,family=binomial)
preds=predict(fit,newdata=list(age=age.grid),se=T)

pfit=exp(preds$fit)/(1+exp(preds$fit))
se.bands.logit = cbind(preds$fit+2*preds$se.fit, preds$fit-2*preds$se.fit)
se.bands = exp(se.bands.logit)/(1+exp(se.bands.logit))

preds=predict(fit,newdata=list(age=age.grid),type="response",se=T)

plot(age,I(wage>250),xlim=agelims,type="n",ylim=c(0,.2))
points(jitter(age), I((wage>250)/5),cex=.5,pch="|",col="darkgrey")
lines(age.grid,pfit,lwd=2, col="blue")
matlines(age.grid,se.bands,lwd=1,col="blue",lty=3)

table(cut(age,4))
fit=lm(wage~cut(age,4),data=Wage)
coef(summary(fit))

```

# Splines

```{r}
library(splines)
fit=lm(wage~bs(age,knots=c(25,40,60)),data=Wage)
pred=predict(fit,newdata=list(age=age.grid),se=T)
summary(fit)

plot(age,wage,col="gray")

lines(age.grid,pred$fit,lwd=2)
#abline(v=c(25,40,60),lty=2,col="darkgreen")
lines(age.grid,pred$fit+2*pred$se,lty="dashed")
lines(age.grid,pred$fit-2*pred$se,lty="dashed")


dim(bs(age,knots=c(25,40,60)))
dim(bs(age,df=6))
attr(bs(age,df=6),"knots")

fit2=lm(wage~ns(age,df=4),data=Wage)
pred2=predict(fit2,newdata=list(age=age.grid),se=T)
lines(age.grid, pred2$fit,col="red",lwd=2)
```

# 6. In this exercise, you will further analyze the Wage data set considered throughout this chapter. 

## (a) Perform polynomial regression to predict wage using age. Use cross-validation to select the optimal degree d for the polynomial. What degree was chosen, and how does this compare to the results of hypothesis testing using ANOVA? Make a plot of the resulting polynomial ﬁt to the data.

```{r}
# ANOVA
fit.1=lm(wage~age,data=Wage)
fit.2=lm(wage~poly(age,2),data=Wage)
fit.3=lm(wage~poly(age,3),data=Wage)
fit.4=lm(wage~poly(age,4),data=Wage)
fit.5=lm(wage~poly(age,5),data=Wage)
anova(fit.1,fit.2,fit.3,fit.4,fit.5)

# cross-validation

library(boot)

##formula 5.2
loocv=function(fit){
  h=lm.influence(fit)$h
  mean((residuals(fit)/(1-h))^2)
}

set.seed(1)
cv.error=rep(0,10)
degree=1:10
for(d in degree){
  glm.fit=glm(wage~poly(age,d),data=Wage)
  cv.error[d]=loocv(glm.fit)
}
plot(degree,cv.error,type = "b")

cv.error10=rep(0,10)
for (i in 1:10){
 glm.fit=glm(wage~poly(age,i),data=Wage)
 cv.error10[i]=cv.glm(Wage,glm.fit,K=10)$delta[1]
 }
cv.error10
plot(degree,cv.error,type = "b")
lines(degree,cv.error10,type = "b", col="red")

```

> ANOVA: degree=3; cross-validation: degree=4 lowest

```{r}
fit=lm(wage~poly(age,4),data=Wage)
summary(fit)

agelims=range(age)
age.grid=seq(from=agelims[1],to=agelims[2]) #min to  max (add 1 each time)
preds=predict(fit,newdata=list(age=age.grid),se=TRUE)# add SE
se.bands=cbind(preds$fit+2*preds$se.fit,preds$fit-2*preds$se.fit)

plot(age,wage,xlim=agelims,cex=.5,col="darkgrey")
title("Degree-4 Polynomial",outer=T)
lines(age.grid,preds$fit,lwd=2,col="blue")
matlines(age.grid,se.bands,lwd=1,col="blue",lty=3)


fit=lm(wage~poly(age,3),data=Wage)
summary(fit)

agelims=range(age)
age.grid=seq(from=agelims[1],to=agelims[2]) #min to  max (add 1 each time)
preds=predict(fit,newdata=list(age=age.grid),se=TRUE)# add SE
se.bands=cbind(preds$fit+2*preds$se.fit,preds$fit-2*preds$se.fit)

plot(age,wage,xlim=agelims,cex=.5,col="darkgrey")
title("Degree-3 Polynomial",outer=T)
lines(age.grid,preds$fit,lwd=2,col="red")
matlines(age.grid,se.bands,lwd=1,col="red",lty=3)
```




## (b) Fit a step function to predict wage using age, and perform cross-validation to choose the optimal number of cuts. Make a plot of the ﬁt obtained.

```{r}
set.seed(1)
cut.cv.error10=rep(0,10)
for (i in 2:10){
 Wage$age.cut <- cut(Wage$age, i) 
 glm.fit=glm(wage~age.cut,data=Wage)
 cut.cv.error10[i]=cv.glm(Wage,glm.fit,K=10)$delta[1]
 }
cut.cv.error10
plot(degree[-1],cut.cv.error10[-1],type = "b")

```

```{r}
plot(wage ~ age, data = Wage, col = "darkgrey")
fit <- lm(wage ~ cut(age, 8), data = Wage)
coef(summary(fit))
preds <- predict(fit, data.frame(age = age.grid))
lines(age.grid, preds, col = "blue", lwd = 2)
```


# 7. The Wage data set contains a number of other features not explored in this chapter, such as marital status (maritl), job class (jobclass), and others. Explore the relationships between some of these other predictors and wage, and use non-linear ﬁtting techniques in order to ﬁt ﬂexible models to the data. Create plots of the results obtained, and write a summary of your ﬁndings.

```{r}
summary(Wage)
library(ggplot2)
library(GGally)
ggpairs(Wage)
```

```{r}
fit.a=lm(wage~maritl,data=Wage)
fit.b=lm(wage~maritl+race,data=Wage)
fit.c=lm(wage~maritl+race+education,data=Wage)
fit.d=lm(wage~maritl+race+education+poly(age, 4),data=Wage)
anova(fit.a,fit.b,fit.c,fit.d)
summary(fit.d)


```


# 8. Fit some of the non-linear models investigated in this chapter to the Auto data set. Is there evidence for non-linear relationships in this data set? Create some informative plots to justify your answer.

```{r}
summary(Auto)
library(ggplot2)
library(GGally)
ggpairs(Auto[-9])


```

```{r}
fit.1=lm(mpg~poly(displacement,4),data=Auto)
summary(fit.1)
fit.1=lm(mpg~poly(displacement,2),data=Auto)
summary(fit.1)
displacementlims=range(Auto$displacement)
displacement.grid=seq(from=displacementlims[1],to=displacementlims[2])
preds=predict(fit.1,newdata=list(displacement=displacement.grid),se=TRUE)
se.bands=cbind(preds$fit+2*preds$se.fit,preds$fit-2*preds$se.fit)
plot(Auto$displacement,Auto$mpg,xlim=displacementlims,cex=.5,col="darkgrey")
title("Degree-2 Polynomial",outer=T)
lines(displacement.grid,preds$fit,lwd=2,col="blue")
matlines(displacement.grid,se.bands,lwd=1,col="blue",lty=3)


fit.2=lm(mpg~poly(horsepower,4),data=Auto)
summary(fit.2)
fit.2=lm(mpg~poly(horsepower,2),data=Auto)
summary(fit.2)
horsepowerlims=range(Auto$horsepower)
horsepower.grid=seq(from=horsepowerlims[1],to=horsepowerlims[2])
preds=predict(fit.2,newdata=list(horsepower=horsepower.grid),se=TRUE)
se.bands=cbind(preds$fit+2*preds$se.fit,preds$fit-2*preds$se.fit)
plot(Auto$horsepower,Auto$mpg,xlim=horsepowerlims,cex=.5,col="darkgrey")
title("Degree-2 Polynomial",outer=T)
lines(horsepower.grid,preds$fit,lwd=2,col="blue")
matlines(horsepower.grid,se.bands,lwd=1,col="blue",lty=3)

fit.3=lm(mpg~poly(weight,4),data=Auto)
summary(fit.3)
fit.3=lm(mpg~poly(weight,2),data=Auto)
summary(fit.3)
weightlims=range(Auto$weight)
weight.grid=seq(from=weightlims[1],to=weightlims[2])
preds=predict(fit.3,newdata=list(weight=weight.grid),se=TRUE)
se.bands=cbind(preds$fit+2*preds$se.fit,preds$fit-2*preds$se.fit)
plot(Auto$weight,Auto$mpg,xlim=weightlims,cex=.5,col="darkgrey")
title("Degree-2 Polynomial",outer=T)
lines(weight.grid,preds$fit,lwd=2,col="blue")
matlines(weight.grid,se.bands,lwd=1,col="blue",lty=3)

fit.4=lm(mpg~poly(displacement,2)+poly(horsepower,2)+poly(weight,2),data=Auto)
summary(fit.4)




```


# 9. This question uses the variables dis (the weighted mean of distances to ﬁve Boston employment centers) and nox (nitrogen oxides concentration in parts per 10 million) from the Boston data. We will treat dis as the predictor and nox as the response.

## (a) Use the poly() function to ﬁt a cubic polynomial regression to predict nox using dis. Report the regression output, and plot the resulting data and polynomial ﬁts.

```{r}
library(MASS)
summary(Boston)

fit.1=lm(nox~poly(dis,3),data=Boston)
summary(fit.1)
dislims=range(Boston$dis)
dis.grid=seq(from=dislims[1],to=dislims[2])
preds=predict(fit.1,newdata=list(dis=dis.grid),se=TRUE)
se.bands=cbind(preds$fit+2*preds$se.fit,preds$fit-2*preds$se.fit)
plot(Boston$dis,Boston$nox,xlim=dislims,cex=.5,col="darkgrey")
title("Degree-3 Polynomial",outer=T)
lines(dis.grid,preds$fit,lwd=2,col="blue")
matlines(dis.grid,se.bands,lwd=1,col="blue",lty=3)


```


## (b) Plot the polynomial ﬁts for a range of diﬀerent polynomial degrees (say, from 1 to 10), and report the associated residual sum of squares.

```{r}
plot(Boston$dis,Boston$nox,xlim=dislims,cex=.5,col="darkgrey")
title("Polynomial",outer=T)
for (i in 1:10){
  fit.1=lm(nox~poly(dis,i),data=Boston)
  preds=predict(fit.1,newdata=list(dis=dis.grid),se=TRUE)
  lines(dis.grid,preds$fit,lwd=2,col=26+i)
  print(summary(fit.1))
 }
```


## (c) Perform cross-validation or another approach to select the optimal degree for the polynomial, and explain your results.

```{r}
# cross-validation

library(boot)
set.seed(1)
cv.error=rep(0,10)
degree=1:10
for(d in degree){
  glm.fit=glm(nox~poly(dis,d),data=Boston)
  cv.error[d]=loocv(glm.fit)
}
cv.error
plot(degree,cv.error,type = "b")

cv.error10=rep(0,10)
for (i in 1:10){
 glm.fit=glm(nox~poly(dis,i),data=Boston)
 cv.error10[i]=cv.glm(Boston,glm.fit,K=10)$delta[1]
 }
cv.error10
plot(degree,cv.error,type = "b")
lines(degree,cv.error10,type = "b", col="red")
```

> optimal degree = 4

## (d) Use the bs() function to ﬁt a regression spline to predict nox using dis. Report the output for the ﬁt using four degrees of freedom. How did you choose the knots? Plot the resulting ﬁt.

```{r}
library(splines)
fit=lm(nox~bs(dis,knots=c(3,5,7)),data=Boston)
pred=predict(fit,newdata=list(dis=dis.grid),se=T)
summary(fit)
plot(Boston$dis,Boston$nox,col="gray")
lines(dis.grid,pred$fit,lwd=2)
lines(dis.grid,pred$fit+2*pred$se,lty="dashed")
lines(dis.grid,pred$fit-2*pred$se,lty="dashed")

dim(bs(Boston$dis,knots=c(3,5,7)))
dim(bs(Boston$dis,df=6))
attr(bs(Boston$dis,df=6),"knots")

fit2=lm(nox~ns(dis,df=4),data=Boston)
pred2=predict(fit2,newdata=list(dis=dis.grid),se=T)
lines(dis.grid, pred2$fit,col="red",lwd=2)
```


## (e) Now ﬁt a regression spline for a range of degrees of freedom, and plot the resulting ﬁts and report the resulting RSS. Describe the results obtained.

```{r}
plot(Boston$dis,Boston$nox,col="gray")
for (i in 1:10){
  fit2=lm(nox~ns(dis,df=i),data=Boston)
  pred2=predict(fit2,newdata=list(dis=dis.grid),se=T)
  lines(dis.grid, pred2$fit,col=1+i,lwd=2)
  print(summary(fit2))
 }
```


## (f) Perform cross-validation or another approach in order to select the best degrees of freedom for a regression spline on this data. Describe your results.

```{r}
# cross-validation

library(boot)
cv.error10=rep(0,10)
for (i in 1:10){
 glm.fit=glm(nox~ns(dis,df=i),data=Boston)
 cv.error10[i]=cv.glm(Boston,glm.fit,K=10)$delta[1]
 }
cv.error10
plot(degree,cv.error10,type = "b", col="red")

```

> the best degrees of freedom for a regression spline on this data = 8