---
title: "chapter9-2"
author: "Min-Yao"
date: "2018年5月4日"
output: 
  html_document: 
    keep_md: yes
---

# from video

```{r}
library(e1071)
# data are not abailable, so I use data from Lab
#video
set.seed(10111)
x=matrix(rnorm(40),20,2)
y=rep(c(-1,1),c(10,10))
x[y==1,]=x[y==1,] + 1
plot(x, col=y+3,pch=19)
dat=data.frame(x,y=as.factor(y))
names(dat)
```
```{r}
make.grid=function(x,n=75){
  grange=apply(x,2,range)
  x1=seq(from=grange[1,1],to=grange[2,1],length=n)
  x2=seq(from=grange[1,2],to=grange[2,2],length=n)
  expand.grid(X1=x1,X2=x2)
}

fit=svm(factor(y)~., data=dat, scale=FALSE,  kernel="radial",cost=5)
xgrid=make.grid(x)
ygrid=predict(fit,xgrid)
plot(xgrid,col=as.numeric(ygrid),pch=20,cex=.2)
points(x,col=y+1,pch=19)
```
```{r}
func=predict(fit,xgrid,decision.values = TRUE)
func=attributes(func)$decision
xgrid=make.grid(x)
ygrid=predict(fit,xgrid)
plot(xgrid,col=as.numeric(ygrid),pch=20,cex=.2)
points(x,col=y+1,pch=19)
xgrid

#contour(xgrid$X1,xgrid$X2,matrix(func,69,99),level = 0, add=TRUE)
#contour(X1,X2,matrix(prob,69,99),level = 0.5, add=TRUE, col="blue",lwd = 2)
```


# Support Vector Machine

```{r}
set.seed(1)
x=matrix(rnorm(200*2), ncol=2)
x[1:100,]=x[1:100,]+2
x[101:150,]=x[101:150,]-2
y=c(rep(1,150),rep(2,50))
dat=data.frame(x=x,y=as.factor(y))
plot(x, col=y)
```

```{r}
train=sample(200,100)
svmfit=svm(y~., data=dat[train,], kernel="radial",  gamma=1, cost=1)
plot(svmfit, dat[train,])
summary(svmfit)
```

```{r}
svmfit=svm(y~., data=dat[train,], kernel="radial",gamma=1,cost=1e5)
plot(svmfit,dat[train,])
```

```{r}
set.seed(1)
tune.out=tune(svm, y~., data=dat[train,], kernel="radial", ranges=list(cost=c(0.1,1,10,100,1000),gamma=c(0.5,1,2,3,4)))
summary(tune.out)
table(true=dat[-train,"y"], pred=predict(tune.out$best.model,newdata=dat[-train,]))
```

# ROC Curves

```{r}
library(ROCR)
rocplot=function(pred, truth, ...){
   predob = prediction(pred, truth)
   perf = performance(predob, "tpr", "fpr")
   plot(perf,...)}
```

```{r}
svmfit.opt=svm(y~., data=dat[train,], kernel="radial",gamma=2, cost=1,decision.values=T)
fitted=attributes(predict(svmfit.opt,dat[train,],decision.values=TRUE))$decision.values
par(mfrow=c(1,2))
rocplot(fitted,dat[train,"y"],main="Training Data")

svmfit.flex=svm(y~., data=dat[train,], kernel="radial",gamma=50, cost=1, decision.values=T)
fitted=attributes(predict(svmfit.flex,dat[train,],decision.values=T))$decision.values
rocplot(fitted,dat[train,"y"],add=T,col="red")

fitted=attributes(predict(svmfit.opt,dat[-train,],decision.values=T))$decision.values
rocplot(fitted,dat[-train,"y"],main="Test Data")
fitted=attributes(predict(svmfit.flex,dat[-train,],decision.values=T))$decision.values
rocplot(fitted,dat[-train,"y"],add=T,col="red")
```

# SVM with Multiple Classes

```{r}
set.seed(1)
x=rbind(x, matrix(rnorm(50*2), ncol=2))
y=c(y, rep(0,50))
x[y==0,2]=x[y==0,2]+2
dat=data.frame(x=x, y=as.factor(y))
par(mfrow=c(1,1))
plot(x,col=(y+1))

svmfit=svm(y~., data=dat, kernel="radial", cost=10, gamma=1)
plot(svmfit, dat)
```

# Application to Gene Expression Data

```{r}
library(ISLR)
names(Khan)
dim(Khan$xtrain)
dim(Khan$xtest)
length(Khan$ytrain)
length(Khan$ytest)

table(Khan$ytrain)
table(Khan$ytest)

dat=data.frame(x=Khan$xtrain, y=as.factor(Khan$ytrain))
out=svm(y~., data=dat, kernel="linear",cost=10)
summary(out)
table(out$fitted, dat$y)
```

```{r}
dat.te=data.frame(x=Khan$xtest, y=as.factor(Khan$ytest))
pred.te=predict(out, newdata=dat.te)
table(pred.te, dat.te$y)
```

## 4. Generate a simulated two-class data set with 100 observations and two features in which there is a visible but non-linear separation between the two classes. Show that in this setting, a support vector machine with a polynomial kernel (with degree greater than 1) or a radial kernel will outperform a support vector classiﬁer on the training data. Which technique performs best on the test data? Make plots and report training and test error rates in order to back up your assertions.

```{r}
set.seed(10111)
x=matrix(rnorm(400),200,2)
y=rep(c(-1,1),c(10,10))
x[y==1,]=x[y==1,] + 2
plot(x, col=y+3,pch=19)
dat=data.frame(x,y=as.factor(y))
dim(dat)
names(dat)
```
```{r}
make.grid=function(x,n=75){
  grange=apply(x,2,range)
  x1=seq(from=grange[1,1],to=grange[2,1],length=n)
  x2=seq(from=grange[1,2],to=grange[2,2],length=n)
  expand.grid(X1=x1,X2=x2)
}

fit=svm(factor(y)~., data=dat, scale=FALSE, kernel="radial",gamma=1,cost=5)
xgrid=make.grid(x)
ygrid=predict(fit,xgrid)
plot(xgrid,col=as.numeric(ygrid),pch=20,cex=.2)
points(x,col=y+1,pch=19)

fit=svm(factor(y)~., data=dat, scale=FALSE,  kernel="polynomial",degree=3 ,cost=5)
xgrid=make.grid(x)
ygrid=predict(fit,xgrid)
plot(xgrid,col=as.numeric(ygrid),pch=20,cex=.2)
points(x,col=y+1,pch=19)
```

```{r}
set.seed(1)
train=sample(200,100)

svmfit=svm(y~., data=dat[train,], scale=FALSE, kernel="radial",gamma=1,cost=5)
plot(svmfit, dat[train,])
summary(svmfit)
table(true=dat[-train,"y"], pred=predict(svmfit,newdata=dat[-train,]))

svmfit=svm(y~., data=dat[train,], scale=FALSE, kernel="polynomial",degree=3 ,cost=5)
plot(svmfit, dat[train,])
summary(svmfit)
table(true=dat[-train,"y"], pred=predict(svmfit,newdata=dat[-train,]))
```

> polynomial is better, which may cause by parameters.

```{r}
set.seed(1)
tune.out=tune(svm, y~., data=dat[train,], kernel="radial", ranges=list(cost=c(0.1,1,10,100,1000),gamma=c(0.5,1,2,3,4)))
summary(tune.out)
table(true=dat[-train,"y"], pred=predict(tune.out$best.model,newdata=dat[-train,]))
```

> radial is better.

## 5. We have seen that we can ﬁt an SVM with a non-linear kernel in order to perform classiﬁcation using a non-linear decision boundary. We will now see that we can also obtain a non-linear decision boundary by performing logistic regression using non-linear transformations of the features.

### (a) Generate a data set with n = 500 and p = 2, such that the observations belong to two classes with a quadratic decision boundary between them. For instance, you can do this as follows:
```{r}
set.seed(1)
x1= runif (500) -0.5
x2= runif (500) -0.5
y=1*( x1^2- x2 ^2 > 0)
dat5a=data.frame(x1,x2,y=as.factor(y))
dim(dat5a)
names(dat5a)
head(dat5a)
```

### (b) Plot the observations, colored according to their class labels.
Your plot should display X 1 on the x-axis, and X 2 on the y-axis.

```{r}
plot(x1,x2, col=y+3,pch=19)
```


### (c) Fit a logistic regression model to the data, using X 1 and X 2 as predictors.

```{r}
glm.fits=glm(y~x1+x2,data=dat5a,family=binomial)
summary(glm.fits)
```


### (d) Apply this model to the training data in order to obtain a predicted class label for each training observation. Plot the observations, colored according to the predicted class labels. The decision boundary should be linear.

```{r}
glm.probs=predict(glm.fits,type="response")
glm.probs[1:10]
glm.pred=rep(1,500)
glm.pred[glm.probs>0.5]=2
table(glm.pred,y)
plot(x1,x2, col=glm.pred,pch=y)

```


### (e) Now ﬁt a logistic regression model to the data using non-linear functions of X 1 and X 2 as predictors (e.g. X 2 1 , X 1 × X 2 , log(X 2 ), and so forth).

```{r}
glm.fits=glm(y~poly(x1,3)+poly(x2,3),data=dat5a,family=binomial)
summary(glm.fits)
```


### (f) Apply this model to the training data in order to obtain a predicted class label for each training observation. Plot the observations, colored according to the predicted class labels. The decision boundary should be obviously non-linear. If it is not, then repeat (a)-(e) until you come up with an example in which the predicted class labels are obviously non-linear.

```{r}
glm.probs=predict(glm.fits,type="response")
glm.probs[1:10]
glm.pred=rep(1,500)
glm.pred[glm.probs>0.5]=2
table(glm.pred,y)
plot(x1,x2, col=glm.pred,pch=y)
```


### (g) Fit a support vector classiﬁer to the data with X 1 and X 2 as predictors. Obtain a class prediction for each training observation. Plot the observations, colored according to the predicted class labels.

```{r}
svmfit=svm(y~x1+x2, data=dat5a, kernel="linear", cost=10, scale=FALSE)
print(svmfit)
plot(svmfit, dat5a)

set.seed(1)
tune.out=tune(svm, y~x1+x2, data=dat5a, kernel="linear", ranges=list(cost=c(0.01,0.1,1,10,100)))
summary(tune.out)

svm.pred=predict(tune.out$best.model,newdata=dat5a)
table(true=y,pred=svm.pred)

plot(x1,x2, col=svm.pred, pch=y)
```


### (h) Fit a SVM using a non-linear kernel to the data. Obtain a class prediction for each training observation. Plot the observations, colored according to the predicted class labels.

```{r}
set.seed(1)
tune.out=tune(svm, y~x1+x2, data=dat5a, kernel="radial", ranges=list(cost=c(0.01,0.1,1,10,100),gamma=c(0.5,1,2,3,4)))
summary(tune.out)

svm.pred=predict(tune.out$best.model,newdata=dat5a)
table(true=y,pred=svm.pred)

plot(x1,x2, col=svm.pred, pch=y)
```


### (i) Comment on your results.

> a SVM using a non-linear kernel and a logistic regression model with non-linear functions are better.

## 7. In this problem, you will use support vector approaches in order to predict whether a given car gets high or low gas mileage based on the Auto data set.

### (a) Create a binary variable that takes on a 1 for cars with gas mileage above the median, and a 0 for cars with gas mileage below the median.

```{r}
library(ISLR)
summary(Auto)
#?Auto
Auto$BI=as.factor(ifelse(Auto$mpg>22.75, 1, 0))
summary(Auto)
```

### (b) Fit a support vector classiﬁer to the data with various values of cost, in order to predict whether a car gets high or low gas mileage. Report the cross-validation errors associated with different values of this parameter. Comment on your results.

```{r}
set.seed(11)
tune.out=tune(svm, BI~., data=Auto, kernel="linear", ranges=list(cost=c(0.1,1,10,100,1000)))
summary(tune.out)

bestmod=tune.out$best.model
summary(bestmod)
```

### (c) Now repeat (b), this time using SVMs with radial and polynomial basis kernels, with diﬀerent values of gamma and degree and cost. Comment on your results.

```{r}
set.seed(11)
tune.out=tune(svm, BI~., data=Auto, kernel="radial", ranges=list(cost=c(0.1,1,10,100,1000),gamma=c(0.5,1,2,3,4)))
summary(tune.out)
bestmod.r=tune.out$best.model
summary(bestmod.r)
svm.pred=predict(bestmod.r,newdata=Auto)
table(true=Auto$BI,pred=svm.pred)

#
tune.out=tune(svm, BI~., data=Auto, kernel="polynomial", ranges=list(cost=c(0.1,1,10,100,1000),degree=c(1,2,3,4,5)))
summary(tune.out)
bestmod.p=tune.out$best.model
summary(bestmod.p)
svm.pred=predict(bestmod.p,newdata=Auto)
table(true=Auto$BI,pred=svm.pred)
```


### (d) Make some plots to back up your assertions in (b) and (c).
Hint: In the lab, we used the plot() function for svm objects
only in cases with p = 2. When p > 2, you can use the plot()
function to create plots displaying pairs of variables at a time.
Essentially, instead of typing

plot(svmfit , dat)

where svmfit contains your ﬁtted model and dat is a data frame
containing your data, you can type

plot(svmfit , dat , x1 ~ x4)

in order to plot just the ﬁrst and fourth variables. However, you
must replace x1 and x4 with the correct variable names. To ﬁnd
out more, type ?plot.svm.


```{r}
names(Auto)
plot(bestmod.r,data=Auto,mpg~cylinders)
plot(bestmod.r,data=Auto,mpg~displacement)
plot(bestmod.r,data=Auto,mpg~horsepower)
plot(bestmod.r,data=Auto,mpg~weight)
plot(bestmod.r,data=Auto,mpg~acceleration)
plot(bestmod.r,data=Auto,mpg~year)
plot(bestmod.r,data=Auto,mpg~origin)
plot(bestmod.p,data=Auto,mpg~cylinders)
plot(bestmod.p,data=Auto,mpg~displacement)
plot(bestmod.p,data=Auto,mpg~horsepower)
plot(bestmod.p,data=Auto,mpg~weight)
plot(bestmod.p,data=Auto,mpg~acceleration)
plot(bestmod.p,data=Auto,mpg~year)
plot(bestmod.p,data=Auto,mpg~origin)

```


## 8. This problem involves the OJ data set which is part of the ISLR package.
### (a) Create a training set containing a random sample of 800 observations, and a test set containing the remaining observations.

```{r}
summary(OJ)
dim(OJ)
set.seed(1)
train=sample(1:nrow(OJ), 800, replace = F)
traindata=OJ[train,]
testdata=OJ[-train,]
summary(traindata)
dim(traindata)
summary(testdata)
dim(testdata)
```

### (b) Fit a support vector classiﬁer to the training data using cost=0.01, with Purchase as the response and the other variables as predictors. Use the summary() function to produce summary statistics, and describe the results obtained.

```{r}
svmfit=svm(Purchase~.,data=traindata, kernel = "linear", cost = 0.01, scale=TRUE)
summary(svmfit)
```

### (c) What are the training and test error rates?

```{r}
# training
pred=predict(svmfit,traindata)
table(predict=pred, truth=traindata$Purchase)
(1-(439+228)/800)*100

# test
pred=predict(svmfit,testdata)
table(predict=pred, truth=testdata$Purchase)
(1-(141+80)/270)*100
```

### (d) Use the tune() function to select an optimal cost. Consider values in the range 0.01 to 10.

```{r}
set.seed(11)
tune.out=tune(svm, Purchase~., data=traindata, scale=TRUE, kernel="linear", ranges=list(cost=c(0.01,0.1,1,10)))
summary(tune.out)

bestmod=tune.out$best.model
summary(bestmod)
```

### (e) Compute the training and test error rates using this new value for cost.

```{r}
# training
pred=predict(bestmod,traindata)
table(predict=pred, truth=traindata$Purchase)
(1-(438+235)/800)*100

# test
pred=predict(bestmod,testdata)
table(predict=pred, truth=testdata$Purchase)
(1-(140+79)/270)*100
```

> 18.89%

### (f) Repeat parts (b) through (e) using a support vector machine with a radial kernel. Use the default value for gamma.

```{r}
#b
svmfit=svm(Purchase~.,data=traindata, kernel = "radial", cost = 0.01, scale=TRUE)
summary(svmfit)

#c
# training
pred=predict(svmfit,traindata)
table(predict=pred, truth=traindata$Purchase)
(1-(494+0)/800)*100

# test
pred=predict(svmfit,testdata)
table(predict=pred, truth=testdata$Purchase)
(1-(159+0)/270)*100
```

```{r}
#d
set.seed(11)
tune.out=tune(svm, Purchase~., data=traindata, kernel="radial", scale=TRUE, ranges=list(cost=c(0.01,0.1,1,10),gamma=c(0.1,0.5,1,2,3,4)))
summary(tune.out)
bestmod=tune.out$best.model
summary(bestmod)

#e
# training
pred=predict(bestmod,traindata)
table(predict=pred, truth=traindata$Purchase)
(1-(455+231)/800)*100

# test
pred=predict(bestmod,testdata)
table(predict=pred, truth=testdata$Purchase)
(1-(142+83)/270)*100

```

> 16.67%

### (g) Repeat parts (b) through (e) using a support vector machine with a polynomial kernel. Set degree=2.

```{r}
#b
svmfit=svm(Purchase~.,data=traindata, kernel = "polynomial", degree=2, cost = 0.01, scale=FALSE)
summary(svmfit)

#c
# training
pred=predict(svmfit,traindata)
table(predict=pred, truth=traindata$Purchase)
(1-(438+235)/800)*100

# test
pred=predict(svmfit,testdata)
table(predict=pred, truth=testdata$Purchase)
(1-(140+80)/270)*100
```

```{r}
#d
set.seed(11)
tune.out=tune(svm, Purchase~., data=traindata, scale=TRUE, kernel="polynomial", ranges=list(cost=c(0.01,0.1,1,10),degree=c(1,2,3,4,5)))
summary(tune.out)
bestmod=tune.out$best.model
summary(bestmod)

#e
# training
pred=predict(bestmod,traindata)
table(predict=pred, truth=traindata$Purchase)
(1-(439+233)/800)*100

# test
pred=predict(bestmod,testdata)
table(predict=pred, truth=testdata$Purchase)
(1-(139+79)/270)*100
```

> 19.25%

### (h) Overall, which approach seems to give the best results on this data?

> linear = 18.89%, radial =  16.67%, polynomial =19.25%, so radial seems to give the best results on this data



