---
title: "chapter8-2"
author: "Min-Yao"
date: "2018年4月9日"
output: 
  html_document: 
    keep_md: yes
---

# Chapter 8 Lab: Decision Trees

# Fitting Classification Trees

```{r}
library(tree)
library(ISLR)
attach(Carseats)
# lab video
hist(Sales)
#
High=ifelse(Sales<=8,"No","Yes")
Carseats=data.frame(Carseats,High)

tree.carseats=tree(High~.-Sales,Carseats)
summary(tree.carseats)
plot(tree.carseats);text(tree.carseats,pretty=0)
tree.carseats

set.seed(2)
train=sample(1:nrow(Carseats), 200)
Carseats.test=Carseats[-train,]
High.test=High[-train]
tree.carseats=tree(High~.-Sales,Carseats,subset=train)
#video
plot(tree.carseats);text(tree.carseats,pretty=0)
#

tree.pred=predict(tree.carseats,Carseats.test,type="class")
#video
with(Carseats[-train,],table(tree.pred,High))
#
table(tree.pred,High.test)
(86+57)/200

set.seed(3)
cv.carseats=cv.tree(tree.carseats,FUN=prune.misclass)
names(cv.carseats)
cv.carseats
#video
plot(cv.carseats)
#

par(mfrow=c(1,2))
plot(cv.carseats$size,cv.carseats$dev,type="b")
plot(cv.carseats$k,cv.carseats$dev,type="b")

prune.carseats=prune.misclass(tree.carseats,best=9)
plot(prune.carseats);text(prune.carseats,pretty=0)

#evaluate in test
tree.pred=predict(prune.carseats,Carseats.test,type="class")
table(tree.pred,High.test)
(94+60)/200

prune.carseats=prune.misclass(tree.carseats,best=15)
plot(prune.carseats);text(prune.carseats,pretty=0)
tree.pred=predict(prune.carseats,Carseats.test,type="class")
table(tree.pred,High.test)
(86+62)/200
```

# Fitting Regression Trees

```{r}
library(MASS)
set.seed(1)
train = sample(1:nrow(Boston), nrow(Boston)/2)
tree.boston=tree(medv~.,Boston,subset=train)
summary(tree.boston)

plot(tree.boston);text(tree.boston,pretty=0)

cv.boston=cv.tree(tree.boston)
plot(cv.boston$size,cv.boston$dev,type='b')

prune.boston=prune.tree(tree.boston,best=5)
plot(prune.boston);text(prune.boston,pretty=0)

yhat=predict(tree.boston,newdata=Boston[-train,])
boston.test=Boston[-train,"medv"]
plot(yhat,boston.test)
abline(0,1)
mean((yhat-boston.test)^2)
```

# Bagging and Random Forests

```{r}
library(MASS)
library(randomForest)
#
dim(Boston)
#
set.seed(1)
train = sample(1:nrow(Boston), nrow(Boston)/2)
#
obb.err=double(13)
test.err=double(13)
for(mtry in 1:13){
  fit=randomForest(medv~.,data=Boston,subset=train,mtry=mtry,ntree=400)
  obb.err[mtry]=fit$mse[400]
  pred=predict(fit,Boston[-train,])
  test.err[mtry]=with(Boston[-train,],mean((medv-pred)^2))
  cat(mtry," ")
}
matplot(1:mtry,cbind(test.err,obb.err),pch = 19,col = c("red","blue"),type = "b",ylab = "Mean squared errors")
legend("topright",legend = c("Test","OOB"),pch = 19,col = c("red","blue"))
#

bag.boston=randomForest(medv~.,data=Boston,subset=train,mtry=13,importance=TRUE)
bag.boston

yhat.bag = predict(bag.boston,newdata=Boston[-train,])
plot(yhat.bag, boston.test)
abline(0,1)
mean((yhat.bag-boston.test)^2)

bag.boston=randomForest(medv~.,data=Boston,subset=train,mtry=13,ntree=25)
yhat.bag = predict(bag.boston,newdata=Boston[-train,])
mean((yhat.bag-boston.test)^2)

set.seed(1)
rf.boston=randomForest(medv~.,data=Boston,subset=train,mtry=6,importance=TRUE)
yhat.rf = predict(rf.boston,newdata=Boston[-train,])
mean((yhat.rf-boston.test)^2)

importance(rf.boston)
varImpPlot(rf.boston)
```

# Boosting

```{r}
library(gbm)
#
boost.boston.v=gbm(medv~.,data=Boston[train,],distribution="gaussian",n.trees=10000,shrinkage = 0.01,interaction.depth=4)
summary(boost.boston.v)
plot(boost.boston.v,i="lstat")
plot(boost.boston.v,i="rm")
#
set.seed(1)
boost.boston=gbm(medv~.,data=Boston[train,],distribution="gaussian",n.trees=5000,interaction.depth=4)
summary(boost.boston)
par(mfrow=c(1,2))
plot(boost.boston,i="rm")
plot(boost.boston,i="lstat")
yhat.boost=predict(boost.boston,newdata=Boston[-train,],n.trees=5000)
mean((yhat.boost-boston.test)^2)
boost.boston=gbm(medv~.,data=Boston[train,],distribution="gaussian",n.trees=5000,interaction.depth=4,shrinkage=0.2,verbose=F)
yhat.boost=predict(boost.boston,newdata=Boston[-train,],n.trees=5000)
mean((yhat.boost-boston.test)^2)
#
n.trees=seq(from=100,to=10000,by=100)
predmat=predict(boost.boston,newdata=Boston[-train,],n.trees=n.trees)
dim(predmat)
berr=with(Boston[-train,],apply((predmat-medv)^2,2,mean))
plot(n.trees,berr,pch=19,ylab = "Mean squared errors",xlab = "# Trees",main =" Bossting Test Error")
abline(h=min(test.err),col="red")

matplot(1:mtry,cbind(test.err,obb.err),pch = 19,col = c("red","blue"),type = "b",ylab = "Mean squared errors")
legend("topright",legend = c("Test","OOB"),pch = 19,col = c("red","blue"))
abline(h=min(test.err),col="red")
#
```

# 5. Suppose we produce ten bootstrapped samples from a data set containing red and green classes. We then apply a classiﬁcation tree to each bootstrapped sample and, for a speciﬁc value of X, produce 10 estimates of P (Class is Red | X): 
0.1, 0.15, 0.2, 0.2, 0.55, 0.6, 0.6, 0.65, 0.7, and 0.75.

There are two common ways to combine these results together into a
single class prediction. One is the majority vote approach discussed in
this chapter. The second approach is to classify based on the average
probability. In this example, what is the ﬁnal classiﬁcation under each
of these two approaches?

```{r}
# The second approach
X=c(0.1, 0.15, 0.2, 0.2, 0.55, 0.6, 0.6, 0.65, 0.7, 0.75)
sum(X)/10
```

> By the first approach (if classiﬁcation is the goal), the ﬁnal classiﬁcation is red.
> By the second approach (if regression is the goal), the ﬁnal classiﬁcation is green.

# 7. In the lab, we applied random forests to the Boston data using mtry=6 and using ntree=25 and ntree=500. Create a plot displaying the test error resulting from random forests on this data set for a more comprehensive range of values for mtry and ntree. You can model your plot after Figure 8.10. Describe the results obtained.



# 8. In the lab, a classiﬁcation tree was applied to the Carseats data set after converting Sales into a qualitative response variable. Now we will seek to predict Sales using regression trees and related approaches, treating the response as a quantitative variable. 

## (a) Split the data set into a training set and a test set.

```{r}
summary(Carseats)

set.seed(10)
train=sample(1:nrow(Carseats), 200)
Carseats.test=Carseats[-train,]
Carseats.train=Carseats[train,]
summary(Carseats.test)
summary(Carseats.train)
```

## (b) Fit a regression tree to the training set. Plot the tree, and interpret the results. What test MSE do you obtain?

```{r}
tree.carseats=tree(Sales~.-High,Carseats,subset=train)
summary(tree.carseats)
plot(tree.carseats);text(tree.carseats,pretty=0)

yhat=predict(tree.carseats,newdata=Carseats.test)
Sales.test=Carseats.test$Sales
plot(yhat,Sales.test)
abline(0,1)
mean((yhat-Sales.test)^2)
```

> MSE = 4.94415

## (c) Use cross-validation in order to determine the optimal level of tree complexity. Does pruning the tree improve the test MSE?

```{r}
cv.carseats=cv.tree(tree.carseats)
cv.carseats
plot(cv.carseats$size,cv.carseats$dev,type='b')

prune.carseats=prune.tree(tree.carseats,best=7)
plot(prune.carseats);text(prune.carseats,pretty=0)

yhat=predict(prune.carseats,newdata=Carseats.test)
Sales.test=Carseats.test$Sales
plot(yhat,Sales.test)
abline(0,1)
mean((yhat-Sales.test)^2)
```

> MSE = 4.419579, better

# 10. We now use boosting to predict Salary in the Hitters data set.

## (a) Remove the observations for whom the salary information is unknown, and then log-transform the salaries.

## (b) Create a training set consisting of the ﬁrst 200 observations, and a test set consisting of the remaining observations.

## (c) Perform boosting on the training set with 1,000 trees for a range of values of the shrinkage parameter λ. Produce a plot with diﬀerent shrinkage values on the x-axis and the corresponding training set MSE on the y-axis.

## (d) Produce a plot with diﬀerent shrinkage values on the x-axis and the corresponding test set MSE on the y-axis.

## (e) Compare the test MSE of boosting to the test MSE that results from applying two of the regression approaches seen in Chapters 3 and 6.

## (f) Which variables appear to be the most important predictors in the boosted model?

## (g) Now apply bagging to the training set. What is the test set MSE for this approach?

# 11. This question uses the Caravan data set.

## (a) Create a training set consisting of the ﬁrst 1,000 observations, and a test set consisting of the remaining observations.

## (b) Fit a boosting model to the training set with Purchase as the response and the other variables as predictors. Use 1,000 trees, and a shrinkage value of 0.01. Which predictors appear to be the most important?

## (c) Use the boosting model to predict the response on the test data. Predict that a person will make a purchase if the estimated probability of purchase is greater than 20 %. Form a confusion matrix. What fraction of the people predicted to make a purchase do in fact make one? How does this compare with the results obtained from applying KNN or logistic regression to this data set?

# 12. Apply boosting, bagging, and random forests to a data set of your choice. Be sure to ﬁt the models on a training set and to evaluate their performance on a test set. How accurate are the results compared to simple methods like linear or logistic regression? Which of these approaches yields the best performance?