---
title: "chapter8-1"
author: "Min-Yao"
date: "2018年4月1日"
output: 
  html_document: 
    keep_md: yes
---

# Chapter 8 Lab: Decision Trees

# Fitting Classification Trees

```{r}
library(tree)
library(ISLR)
attach(Carseats)
# lab video
hist(Sales)
#
High=ifelse(Sales<=8,"No","Yes")
Carseats=data.frame(Carseats,High)

tree.carseats=tree(High~.-Sales,Carseats)
summary(tree.carseats)
plot(tree.carseats);text(tree.carseats,pretty=0)
tree.carseats

set.seed(2)
train=sample(1:nrow(Carseats), 200)
Carseats.test=Carseats[-train,]
High.test=High[-train]
tree.carseats=tree(High~.-Sales,Carseats,subset=train)
#video
plot(tree.carseats);text(tree.carseats,pretty=0)
#

tree.pred=predict(tree.carseats,Carseats.test,type="class")
#video
with(Carseats[-train,],table(tree.pred,High))
#
table(tree.pred,High.test)
(86+57)/200

set.seed(3)
cv.carseats=cv.tree(tree.carseats,FUN=prune.misclass)
names(cv.carseats)
cv.carseats
#video
plot(cv.carseats)
#

par(mfrow=c(1,2))
plot(cv.carseats$size,cv.carseats$dev,type="b")
plot(cv.carseats$k,cv.carseats$dev,type="b")

prune.carseats=prune.misclass(tree.carseats,best=9)
plot(prune.carseats);text(prune.carseats,pretty=0)

#evaluate in test
tree.pred=predict(prune.carseats,Carseats.test,type="class")
table(tree.pred,High.test)
(94+60)/200

prune.carseats=prune.misclass(tree.carseats,best=15)
plot(prune.carseats);text(prune.carseats,pretty=0)
tree.pred=predict(prune.carseats,Carseats.test,type="class")
table(tree.pred,High.test)
(86+62)/200
```

# Fitting Regression Trees

```{r}
library(MASS)
set.seed(1)
train = sample(1:nrow(Boston), nrow(Boston)/2)
tree.boston=tree(medv~.,Boston,subset=train)
summary(tree.boston)

plot(tree.boston);text(tree.boston,pretty=0)

cv.boston=cv.tree(tree.boston)
plot(cv.boston$size,cv.boston$dev,type='b')

prune.boston=prune.tree(tree.boston,best=5)
plot(prune.boston);text(prune.boston,pretty=0)

yhat=predict(tree.boston,newdata=Boston[-train,])
boston.test=Boston[-train,"medv"]
plot(yhat,boston.test)
abline(0,1)
mean((yhat-boston.test)^2)
```

# 1. Draw an example (of your own invention) of a partition of two-dimensional feature space that could result from recursive binary splitting. Your example should contain at least six regions. Draw a decision tree corresponding to this partition. Be sure to label all aspects of your ﬁgures, including the regions R 1 , R 2 , . . ., the cutpoints t 1 , t 2 , . . ., and so forth.
Hint: Your result should look something like Figures 8.1 and 8.2.

> in the tree for Q1 floder

# 3. Consider the Gini index, classiﬁcation error, and entropy in a simple classiﬁcation setting with two classes. Create a single plot that displays each of these quantities as a function of ˆp m1 . The x-axis should display ˆp m1 , ranging from 0 to 1, and the y-axis should display the value of the Gini index, classiﬁcation error, and entropy. 
Hint: In a setting with two classes, ˆp m1 = 1 − ˆp m2 . You could make this plot by hand, but it will be much easier to make in R.

```{r}
pm1=seq(0,1,by=0.01)
E=1-pm1
plot(pm1,E)

G=pm1*(1-pm1)
plot(pm1,G)

D=-(pm1*log10(pm1))
plot(pm1,D)

```


# 8. In the lab, a classiﬁcation tree was applied to the Carseats data set after converting Sales into a qualitative response variable. Now we will seek to predict Sales using regression trees and related approaches, treating the response as a quantitative variable. 

## (a) Split the data set into a training set and a test set.

```{r}
summary(Carseats)

set.seed(10)
train=sample(1:nrow(Carseats), 200)
Carseats.test=Carseats[-train,]
Carseats.train=Carseats[train,]
summary(Carseats.test)
summary(Carseats.train)
```

## (b) Fit a regression tree to the training set. Plot the tree, and interpret the results. What test MSE do you obtain?

```{r}
tree.carseats=tree(Sales~.-High,Carseats,subset=train)
summary(tree.carseats)
plot(tree.carseats);text(tree.carseats,pretty=0)

yhat=predict(tree.carseats,newdata=Carseats.test)
Sales.test=Carseats.test$Sales
plot(yhat,Sales.test)
abline(0,1)
mean((yhat-Sales.test)^2)

```

> MSE = 4.94415

## (c) Use cross-validation in order to determine the optimal level of tree complexity. Does pruning the tree improve the test MSE?

```{r}
cv.carseats=cv.tree(tree.carseats)
cv.carseats
plot(cv.carseats$size,cv.carseats$dev,type='b')

prune.carseats=prune.tree(tree.carseats,best=7)
plot(prune.carseats);text(prune.carseats,pretty=0)

yhat=predict(prune.carseats,newdata=Carseats.test)
Sales.test=Carseats.test$Sales
plot(yhat,Sales.test)
abline(0,1)
mean((yhat-Sales.test)^2)
```

> MSE = 4.419579, better

# 9. This problem involves the OJ data set which is part of the ISLR package.

```{r}
library(ISLR)
summary(OJ)
```

## (a) Create a training set containing a random sample of 800 observations, and a test set containing the remaining observations.

```{r}
set.seed(10)
train=sample(1:nrow(OJ), 800)
OJ.test=OJ[-train,]
OJ.train=OJ[train,]
summary(OJ.test)
summary(OJ.train)
dim(OJ)
dim(OJ.test)
dim(OJ.train)
```

## (b) Fit a tree to the training data, with Purchase as the response and the other variables as predictors. Use the summary() function to produce summary statistics about the tree, and describe the results obtained. What is the training error rate? How many terminal nodes does the tree have?

```{r}
tree.OJ=tree(Purchase~.,OJ,subset=train)
summary(tree.OJ)
```

> Number of terminal nodes:  7

> Misclassification error rate: 0.1625

## (c) Type in the name of the tree object in order to get a detailed text output. Pick one of the terminal nodes, and interpret the information displayed.

```{r}
tree.OJ
?OJ
```

> 4) LoyalCH < 0.276142 172  119.500 MM ( 0.11047 0.88953 ) *

> when customer brand loyalty for Citrus Hill is less than 0.276142, 88.953% customer purchased Minute Maid Orange Juice and 11.047% customer purchased Citrus Hill.

## (d) Create a plot of the tree, and interpret the results.

```{r}
plot(tree.OJ);text(tree.OJ,pretty=0)
```

> Customer brand loyalty for CH (LoyalCH) and Sale price of MM less sale price of CH (PriceDiff) are important.

## (e) Predict the response on the test data, and produce a confusion matrix comparing the test labels to the predicted test labels. What is the test error rate?

```{r}
tree.pred=predict(tree.OJ,OJ.test,type="class")
purchase.test=OJ.test$Purchase
table(tree.pred,purchase.test)
(155+66)/270
1-((155+66)/270)
```

> the test error rate = 18.1%

## (f) Apply the cv.tree() function to the training set in order to determine the optimal tree size.

```{r}
cv.OJ=cv.tree(tree.OJ,FUN=prune.misclass)
names(cv.OJ)
cv.OJ
plot(cv.OJ)
```



## (g) Produce a plot with tree size on the x-axis and cross-validated classiﬁcation error rate on the y-axis.

```{r}
plot(cv.OJ$size,cv.OJ$dev,type="b")
```


## (h) Which tree size corresponds to the lowest cross-validated classiﬁcation error rate?

> size 5 orresponds to the lowest cross-validated classiﬁcation error rate

## (i) Produce a pruned tree corresponding to the optimal tree size obtained using cross-validation. If cross-validation does not lead to selection of a pruned tree, then create a pruned tree with ﬁve terminal nodes.

```{r}
prune.OJ=prune.misclass(tree.OJ,best=5)
plot(prune.OJ);text(prune.OJ,pretty=0)

```

## (j) Compare the training error rates between the pruned and un-pruned trees. Which is higher?

```{r}
summary(tree.OJ)
summary(prune.OJ)
```

> the training error rates of the pruned trees is higher

## (k) Compare the test error rates between the pruned and unpruned trees. Which is higher?

```{r}
tree.pred=predict(tree.OJ,OJ.test,type="class")
table(tree.pred,purchase.test)
(155+66)/270
1-((155+66)/270)

prune.pred=predict(prune.OJ,OJ.test,type="class")
table(prune.pred,purchase.test)
(151+68)/270
1-((151+68)/270)
```

> the test error rates of the pruned trees is higher, but almost the same