---
title: "chapter4-2"
author: "Min-Yao"
date: "2018年1月22日"
output: 
  html_document: 
    keep_md: yes
---

# Linear Discriminant Analysis

```{r}
library(ISLR)
library(MASS)
attach(Smarket)
train=(Year<2005)
Smarket.2005=Smarket[!train,]
dim(Smarket.2005)
Direction.2005=Direction[!train]

lda.fit=lda(Direction~Lag1+Lag2,data=Smarket,subset=train)
lda.fit
plot(lda.fit)

#Smarket.2005=subset(Smarket, Year==2005)

lda.pred=predict(lda.fit, Smarket.2005)
names(lda.pred)
lda.class=lda.pred$class
table(lda.class,Direction.2005)
mean(lda.class==Direction.2005)
sum(lda.pred$posterior[,1]>=.5)
sum(lda.pred$posterior[,1]<.5)
lda.pred$posterior[1:20,1]
lda.class[1:20]
sum(lda.pred$posterior[,1]>.9)
```

# 10. This question should be answered using the Weekly data set, which is part of the ISLR package. This data is similar in nature to the Smarket data from this chapter’s lab, except that it contains 1, 089 weekly returns for 21 years, from the beginning of 1990 to the end of
2010.
## (a) Produce some numerical and graphical summaries of the Weekly data. Do there appear to be any patterns?

```{r}
library(ISLR)
names(Weekly)
dim(Weekly)
summary(Weekly)
pairs(Weekly)

cor(Weekly[,-9])
attach(Weekly)
plot(Volume)
```

>  Volume is increasing over time but decreasing recently.  In other words, the average number of shares traded daily increased and then decreased.

## (b) Use the full data set to perform a logistic regression with Direction as the response and the ﬁve lag variables plus Volume as predictors. Use the summary function to print the results. Do any of the predictors appear to be statistically signiﬁcant? If so, which ones?

```{r}
glm.fits.Weekly=glm(Direction~Lag1+Lag2+Lag3+Lag4+Lag5+Volume,data=Weekly,family=binomial)
summary(glm.fits.Weekly)

coef(glm.fits.Weekly)
summary(glm.fits.Weekly)$coef
```

> Yes, Lag2 appears to be statistically signiﬁcant.

## (c) Compute the confusion matrix and overall fraction of correct predictions. Explain what the confusion matrix is telling you about the types of mistakes made by logistic regression.

```{r}
glm.probs.Weekly=predict(glm.fits.Weekly,type="response")

glm.pred.Weekly=rep("Down",1089)
glm.pred.Weekly[glm.probs.Weekly>.5]="Up"
table(glm.pred.Weekly,Direction)

(54+557)/1089
mean(glm.pred.Weekly==Direction)
```

> 430 type I error (false positive), 48 type II error (false negative)

## (d) Now ﬁt the logistic regression model using a training data period from 1990 to 2008, with Lag2 as the only predictor. Compute the confusion matrix and the overall fraction of correct predictions for the held out data (that is, the data from 2009 and 2010).

```{r}
train.1990to2008=(Year<2009)
Weekly.2009to2010=Weekly[!train.1990to2008,]
dim(Weekly.2009to2010)
Direction.1990to2008=Direction[!train.1990to2008]

glm.fits.Lag2=glm(Direction~Lag2,data=Weekly,family=binomial,subset=train.1990to2008)

glm.probs=predict(glm.fits.Lag2,Weekly.2009to2010,type="response")

glm.pred=rep("Down",104)
glm.pred[glm.probs>.5]="Up"
table(glm.pred,Direction.1990to2008)
mean(glm.pred==Direction.1990to2008)
(9+56)/104

```

> 62.5%  accuracy rate

## (e) Repeat (d) using LDA.

```{r}
lda.fit.train=lda(Direction~Lag2,data=Weekly,subset=train.1990to2008)
lda.fit.train
plot(lda.fit.train)

lda.pred.test=predict(lda.fit.train, Weekly.2009to2010)
names(lda.pred.test)
lda.class=lda.pred.test$class
table(lda.class,Direction.1990to2008)
mean(lda.class==Direction.1990to2008)

```

> the same 62.5%  accuracy rate

# 11. In this problem, you will develop a model to predict whether a given car gets high or low gas mileage based on the Auto data set.

## (a) Create a binary variable, mpg01, that contains a 1 if mpg contains a value above its median, and a 0 if mpg contains a value below its median. You can compute the median using the median() function. Note you may ﬁnd it helpful to use the data.frame() function to create a single data set containing both mpg01 and the other Auto variables.

```{r}
library(ISLR)
names(Auto)

dim(Auto)
summary(Auto)

attach(Auto)
median(mpg)
#22.75

mpg01=rep(0,392)
mpg01[mpg>22.75]=1
summary(mpg01)

str(Auto)

new.Auto <- cbind(Auto, mpg01)
#new.Auto
str(new.Auto)

```

## (b) Explore the data graphically in order to investigate the association between mpg01 and the other features. Which of the other features seem most likely to be useful in predicting mpg01? Scatterplots and boxplots may be useful tools to answer this question. Describe your ﬁndings.

```{r}
summary(new.Auto)
pairs(new.Auto)
#cor(new.Auto)
cor(new.Auto[,-9])

glm.fits.new.Auto=glm(mpg01~.-name,data=new.Auto,family=binomial)
summary(glm.fits.new.Auto)

coef(glm.fits.new.Auto)
summary(glm.fits.new.Auto)$coef
```

> Except mpg, horsepower and year seem most likely to be useful in predicting mpg01, and displacement, acceleration, and origin may also be useful in predicting mpg01.

## (c) Split the data into a training set and a test set.

```{r}
summary(new.Auto)
dim(new.Auto)
attach(new.Auto)
train=(weight<3000)
test = new.Auto[!train,]
dim(test)
summary(test)
training = new.Auto[train,]
dim(training)
summary(training)

mpg01.test=mpg01[!train]
```

## (d) Perform LDA on the training data in order to predict mpg01 using the variables that seemed most associated with mpg01 in (b). What is the test error of the model obtained?

```{r}
lda.fit.horsepower=lda(mpg01~horsepower,data=new.Auto,subset=train)
lda.fit.horsepower
plot(lda.fit.horsepower)

lda.pred.horsepower=predict(lda.fit.horsepower, test)
names(lda.pred.horsepower)

lda.class.horsepower=lda.pred.horsepower$class
table(lda.class.horsepower,mpg01.test)
mean(lda.class.horsepower==mpg01.test)
test_error=1-mean(lda.class.horsepower==mpg01.test)
test_error
#

lda.fit.mpg=lda(mpg01~mpg,data=new.Auto,subset=train)
lda.fit.mpg
plot(lda.fit.mpg)

lda.pred.mpg=predict(lda.fit.mpg, test)
names(lda.pred.mpg)

lda.class.mpg=lda.pred.mpg$class
table(lda.class.mpg,mpg01.test)
mean(lda.class.mpg==mpg01.test)
test_error=1-mean(lda.class.mpg==mpg01.test)
test_error
```


## (f) Perform logistic regression on the training data in order to predict mpg01 using the variables that seemed most associated with mpg01 in (b). What is the test error of the model obtained?

```{r}
glm.fits.horsepower=glm(mpg01~horsepower,data=new.Auto,family=binomial,subset=train)

glm.probs=predict(glm.fits.horsepower,test,type="response")

glm.pred=rep("0",167)
glm.pred[glm.probs>0.5]="1"
table(glm.pred,mpg01.test)
mean(glm.pred==mpg01.test)
test_error=1-mean(glm.pred==mpg01.test)
test_error

#

glm.fits.mpg=glm(mpg01~mpg,data=new.Auto,family=binomial,subset=train)

glm.probs=predict(glm.fits.mpg,test,type="response")

glm.pred=rep("0",167)
glm.pred[glm.probs>0.5]="1"
table(glm.pred,mpg01.test)
mean(glm.pred==mpg01.test)
test_error=1-mean(glm.pred==mpg01.test)
test_error

```